---
title: "Data Import"
author: "Priyal"
date: "9/18/2018"
output: html_document
---

```{r setup, include=FALSE
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


###Import FAS csv files

Import my first csv (FAS_litters)

```{r}
litters_data = read_csv(file = "./data/FAS_litters.csv")
litters_data = janitor::clean_names(litters_data)
```

Learning Assessment: Importing pups data

```{r}
pups_data = read_csv(file = "./data/FAS_pups.csv")
```

### Look at data

Look at litters data.
```{r}
head(litters_data)
tail(litters_data)

skimr::skim(litters_data)
```

Skip some rows

```{r}
litters_data = read_csv(file = "./data/FAS_litters.csv",
  skip = 10, col_names = FALSE)
```

###Parsing columns

```{r}
litters_data = read_csv(file = "./data/FAS_litters.csv",
  col_types = cols(
    Group = col_character(),
    `Litter Number` = col_character(),
    `GD0 weight` = col_double(),
    `GD18 weight` = col_double(),
    `GD of Birth` = col_integer(),
    `Pups born alive` = col_integer(),
    `Pups dead @ birth` = col_integer(),
    `Pups survive` = col_integer()
  )
)
litters_data = read_csv(file = "./data/FAS_litters.csv",
              col_types = "ccddiiii"
)
```

Look at pups data

```{r}
head(pups_data)
tail(pups_data)
```

```{r}
pups_data = read_csv(file = "./data/FAS_pups.csv",col_types = "ciiiii")
pups_data = janitor::clean_names(pups_data)
skimr::skim(pups_data)
```

To read in csv we used read_csv (file = "relative path.csv")

### Other formats

Read in mlb data

```{r}
library(readxl)
mlb_data = read_excel(path = "./data/mlb11.xlsx")
```
For excel we are using path = or simply read_excel(relative path.xlsx)

Read in data from SAS, Stata and SPSS:

```{r}
pulse_data = haven::read_sas("./data/public_pulse_data.sas7bdat")
```

Either first load the whole package with library(haven) or to use a specific function haven::read_sas

Importing Fas_pups using read.csv
```{r}
pups_base = read.csv("./data/fas_pups.csv")
pups_readr = read_csv(file = "./data/fas_pups.csv")
pups_readr = janitor::clean_names(pups_data1)

pups_base$s
pups_readr$S
```


