---
title: "tidy_data"
author: "Priyal"
date: "9/25/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
options(tibble.print_min = 5)
```


##Import dataset PULSE 

```{r}
pulse_data = 
  haven::read_sas("./data/public_pulse_data.sas7bdat") %>%
  janitor::clean_names()
```

Gather

```{r}
pulse_tidy_data = gather(pulse_data, key = visit, value = bdi, bdi_score_bl:bdi_score_12m)
```

separate

```{r}
separate(pulse_tidy_data, visit, into = c("remove_1", "remove_2", "visit"), sep = "_") 
```

Import, tidy and transform Pulse dataset

```{r}
pulse_data = 
  haven::read_sas("./data/public_pulse_data.sas7bdat") %>%
  janitor::clean_names() %>%
  gather(key = visit, value = bdi, bdi_score_bl:bdi_score_12m) %>%
  separate(visit, into = c("remove_1", "remove_2", "visit"), sep = "_") %>%
  select(id, visit, everything(), -starts_with("remove")) %>%
  mutate(visit = replace(visit, visit == "bl", "00m"), 
         visit = factor(visit, levels = str_c(c("00", "01", "06", "12"), "m"))) %>% 
  arrange(id, visit)
print(pulse_data, n = 12)
  
```


## Revisit FAS_litters

Counting groups

```{r}
litters_data = read_csv("./data/FAS_litters.csv", col_types = "ccddiiii") %>% janitor::clean_names() %>%
  count(group)
```



```{r}
litters_data = 
  read_csv("./data/FAS_litters.csv", col_types = "ccddiiii") %>%
  janitor::clean_names() %>%
  separate(group, into = c("dose", "day_of _tx"),sep = 3) %>%
  mutate(dose = tolower(dose), wt_gain = gd18_weight - gd0_weight) %>% 
  arrange(litter_number)
```

Learning Assessment 1

```{r}
litters_data %>% 
  select(litter_number, ends_with("weight")) %>% 
  gather(key = gd, value = weight, gd0_weight:gd18_weight) %>% 
  mutate(gd = recode(gd, "gd0_weight" = 0, "gd18_weight" = 18)) %>% 
  arrange(litter_number)
```


Create analysis_result

```{r}
analysis_result = tibble(
  group = c("treatment", "treatment", "placebo", "placebo"),
  time = c("pre", "post", "pre", "post"),
  mean = c(4, 8, 3.5, 4)
)

```

Make it readable

```{r}
analysis_result %>%
  spread(key = time , value = mean) %>% 
  knitr::kable()
```


##Importing data from xl

Cleaning non tidy data across multiple tables, 
Stacking to produce clead data

```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") %>%
  mutate(movie = "fellowship_ring")

two_towers = readxl::read_excel("./data/LotR_Words.xlsx", range = "F3:H6") %>%
  mutate(movie = "two_towers")

return_king = readxl::read_excel("./data/LotR_Words.xlsx", range = "J3:L6") %>%
  mutate(movie = "return_king")
```

Binding rows

```{r}
lotr_data = bind_rows(fellowship_ring, two_towers, return_king) %>%
  janitor::clean_names() %>%
  gather(key = sex, value = word, female:male) %>%
  mutate(race = tolower(race)) %>% 
  select(movie, everything()) 
```

Joining datasets

```{r}
  pup_data = read_csv("./data/FAS_pups.csv", col_types = "ciiiii") %>%
  janitor::clean_names() %>%
  mutate(sex = recode(sex, `1` = "male", `2` = "female")) 
  
litter_data = read_csv("./data/FAS_litters.csv", 
              col_types = "ccddiiii") %>%
  janitor::clean_names() %>%
  select(-pups_survive) %>%
  mutate(
  wt_gain = gd18_weight - gd0_weight,
  group = tolower(group))
```

Create joined data

```{r}
FAS_data = left_join(pup_data, litter_data, by = "litter_number")
```

Learning Assessment 2

```{r}
survey_os = read_csv("./data/survey_results/surv_os.csv", col_types = "cc") %>%
  janitor::clean_names() %>% 
  rename(id = what_is_your_uni, os =  what_operating_system_do_you_use)
  
survey_git = read_csv("./data/survey_results/surv_program_git.csv", col_types = "ccc") %>%
  janitor::clean_names() %>% 
  rename(id = what_is_your_uni, 
         prog = what_is_your_degree_program,
         git_exp = which_most_accurately_describes_your_experience_with_git)

```

Joining the data sets

```{r}
Left_join = left_join(survey_os, survey_git)
Inner_join = inner_join(survey_os, survey_git)
anti_join1 = anti_join(survey_os, survey_git)
anti_join2 = anti_join(survey_git, survey_os)
```



